---
title: "R Markdown Example"
author: "Arne Pommerening"
date: "1 November 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
This is a section header. Demonstration of markdown features.


### Lists and other things

+ Packages
    + markdown
    + knitr
+ Output
    + pdf
    + HTML
    + word

1. Packages
    1. rmarkdown
    1. knitr
    1. ggplot2
3. Output
    1. Pdf
    2. HTML
    2. Word

This is Text. This word is **bold**. And here there is one printed in *italics*.

Underscores are also possible:

* __bold__
* _italics_ using underscores \_
* ~~strike~~
* standard

### Links

https://github.com/apommerening/Scientific-Computing-Drop-In

[Arne's github repository for the drop-in sessions](https://github.com/apommerening/Scientific-Computing-Drop-In)

[Markdown cheat sheet 1] (https://www.markdownguide.org/cheat-sheet/)

[Markdown cheat sheet 2] (https://en.support.wordpress.com/markdown-quick-reference/)

### Equations (use Latex syntax)

$\overline{d} = \frac{1}{k} \sum_{i = 1}^k d_i$


## Including data and calculations

```{r echo = TRUE}
myData <- read.table("Allmitwald.txt", header = T)		
dim(myData)										
names(myData)										
```

Note you can set `echo = FALSE` in the code chunk to prevent printing of the R code that generated the plot:

```{r echo = FALSE}
myData <- read.table("Allmitwald.txt", header = T)		
dim(myData)										
names(myData)										
```

Number of trees per plot:


```{r echo = FALSE}
tapply(myData$treeNumber, myData$plotNumber, length)		

```

Number of species (BE - beech, NS - Norway spruce, SF - silver fir, SP - Scots pine):
```{r echo = TRUE}
table(myData$species)		


```
Mean and range of h/d ratios:
```{r echo = TRUE}
mean(100 * myData$height / myData$dbh)		
range(100 * myData$height / myData$dbh)		
```

## Including Plots

You can also embed plots, for example the empirical stem diameter distribution:

First let's check the stem diameter range:
```{r echo = TRUE}
range(myData$dbh)
```

Now let's plot the empirical distribution:

```{r echo = FALSE}
hist1 <- hist(myData$dbh, include.lowest = TRUE, right = FALSE, plot = FALSE, breaks = seq(8, 84, by = 4))#
hist1$counts <- hist1$counts / length(myData$dbh)
par(mar = c(2, 4, 1, 2))
plot(hist1, las = 1, cex.axis = 1.2, lwd = 2, ylim = c(0, 0.25), main = "", xlab = "", ylab = "") 
```

Of course, it makes sense to include some text on your interpretation here. For example you could note that the stem diameter distribution is bimodal and that it might be a good idea to find out what species contribute to which mode.

And to have a map of one of the plots may also be helpful:

```{r echo = FALSE}
# install.packages("plotrix", dep = T)
library(plotrix)
myData$x <- myData$distance * sin(myData$azimuth * pi / 180)
myData$y <- myData$distance * cos(myData$azimuth * pi / 180)
myData$colour <- "brown" 
myData$colour[myData$species == "BE"] <- "red" 
myData$colour[myData$species == "SF"] <- "purple" 
myData$colour[myData$species == "SP"] <- "orange" 
plotNumber <- 1
plotString <- paste("Plot", toString(plotNumber), sep=" ")
myData.onePlot <- subset(myData, myData$plotNumber == plotNumber)			
radius <- myData.onePlot$radius[1]

par(mar = c(2, 0, 2, 0))
plot(myData.onePlot$x, myData.onePlot$y, xlab = "", ylab = "", cex = 5 * myData.onePlot$dbh/max(myData$dbh), las = 1, axes = FALSE, xlim = c(-radius - 1, radius + 1), ylim = c(-radius - 1, radius + 1), asp = 1, main = plotString, col = myData.onePlot$colour, lwd = 2) 
# for (i in 1 : length(myData.onePlot$treeNumber))  
#  text(myData.onePlot$x[i] + 1.6 * myData.onePlot$dbh[i]/max(myData$dbh), myData.onePlot$y[i]- 2.0 *  myData.onePlot$dbh[i]/max(myData$dbh), myData.onePlot$treeNumber[i], cex = .8, pos = 2, col = "black") # 1.6 0.8
draw.circle(0, 0, myData.onePlot$radius[1], nv = 100, lty = 1,lwd = 2) 
axis(1, lwd = 2, cex.axis = 1.3)
legend("right", inset = 0, title = "",c("BE", "NS", "SF", "SP"), fill = c("red", "brown", "purple", "orange"), bty = "n", cex = 1.3)
```

